Codebook created on 2021-11-10 at 2021-11-10 14:59:00

### 2021-11-10 codebook_tris.Rmd
add tris' data for exploratory analysis

---
title: "Codebook created on 2021-11-05 at 2021-11-05 12:55:43"
output: github_document
---

@@

## Dataset description
The data contains 401 cases and 43 variables.

@@

```{r}
summaries <- read.csv("./codebook_nl.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2021-11-10 at 2021-11-10 14:59:00"
output: github_document
---

@@

## Dataset description
The data contains 1337 cases and 33 variables.

@@

```{r}
summaries <- read.csv("./codebook_tris.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```
